\texttt{davos}: The Python package smuggler

### 2022-04-07 paper/main.tex
reorganized source to 1 sentence per line, recompiled pdf

\begin{abstract}
% 100-word limit (though many published articles don't seem to conform to this?)
% \texttt{davos} is a Python package for creating self-managing, reproducible workflows that specify dependencies directly in their code, and install them 
% \texttt{davos} is a Python package that enables creating and sharing reproducible workflows as a single, ready-to-run IPython notebook. 
\texttt{davos} is a Python package for sharing

\end{abstract}

@@

One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications. Researchers can then share these environments alongside their code as configuration files that explicitly list required packages and versions, enabling other users to build identical copies for themselves. However, this approach comes with two major drawbacks: First, it can add significantly to the technical knowledge, system resources, and initial setup required to share and run the actual code of interest. For example, sharing research code that relies on a particular Docker image to run properly not only necessitates distributing extra configuration files and setup instructions, but also requires that both the original author and anyone with whom the code may be shared install and navigate additional software that is likely more complex and resource-intensive than the Python code it supports. These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity among scientists, and can create significant barriers to both contributing to and taking advantage of open science resources.

%Second, typical environment management tools don't enforce that specified requirements \textit{remain} satisfied after they are initially installed. This makes it easy to inadvertently alter existing packages in a Python environment at any point in time, potentially affecting the behavior of code that depends on them. For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}." If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgrade to accommodate this new requirement. potentially altering or breaking the previous analyses  in future runs, as well as for anyone with whom  analysis code. Further, if earlier analyses require functionality

>>>>

\begin{abstract}
% 100-word limit (though many published articles don't seem to conform to this?)
\end{abstract}

@@

One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications. 
Researchers can then share these environments alongside their code as configuration files that explicitly list required package versions, enabling other users to build identical copies for themselves. 
While often effective, this approach comes with two notable drawbacks: 
First, it can add significantly to the technical knowledge, system resources, and initial setup required to share and run the actual code of interest. 
For example, sharing research code that relies on a particular Docker image to run properly not only necessitates distributing extra configuration files and setup instructions, but also requires that both the original author and anyone with whom the code may be shared install and navigate additional software that is likely more complex and resource-intensive than the Python code it is used to manage. 
These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity, and can create significant barriers to both contributing to and taking advantage of open science resources.

%Second, typical environment management tools don't enforce that specified requirements \textit{remain} satisfied after they are initially installed. 
%This makes it easy to inadvertently alter existing packages in a Python environment at any point in time, potentially affecting the behavior of code that depends on them. 
%For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}." 
%If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgrade to accommodate this new requirement, potentially altering or breaking the previous analyses in future runs, as well as for anyone with whom  analysis code. 
%Further, if earlier analyses require functionality
